\newpage
\section{Motivating Example}
\label{sec:overview}

In this section, we motivate our idea of context tunneling with a simple example. We
explain our technique in the context of call-site-sensitivity, but it
is also applicable
to other flavors of context-sensitivity too, such as object-sensitivity and
type-sensitivity. The general description is presented in
Section~\ref{sec:tunneling}.

\myparagraph{Example Code}

Suppose that we analyze the example Java code in
Fig.~\ref{fig:overview}(a) using a $k$-call-site-sensitive points-to
analysis~\cite{Smaragdakis2015}.  The example code has three class
definitions, namely \texttt{A}, \texttt{B}, and \texttt{C}.  Classes
\texttt{A} and \texttt{B} are empty and class \texttt{C} has two
methods: \texttt{id} and \texttt{main}.  Method \texttt{id} is
essentially an identity function on the first argument, which takes an
object \texttt{v} and an integer \texttt{i}, and returns the same
object after making recursive calls until \texttt{i} becomes 0. In
\texttt{main}, \texttt{id} is invoked twice with different
objects. Both method invocations share the same argument \texttt{i}
that comes from the external environment (i.e. user input).  The goal
of the points-to analysis is to prove the safety of two type casts at
lines 8 and 9.

\begin{figure}
\centering
\begin{subfigure}[b]{.45\columnwidth}
\begin{lstlisting}
class A {} class B {}
class C {
  static Object id (Object v, int i){
      return i >= 0 ? id(v, i-1) : v;
  }
  public static void main (){
    int i = input();
    A a = (A) id(new A(), i);	//Query 1
    B b = (B) id(new B(), i);	//Query 2
  }
}
\end{lstlisting}
\caption{Example code}
\label{fig:overview:code}
\end{subfigure}
\quad
\begin{subfigure}[b]{.45\columnwidth}

%%% k-CFA
\begin{center}
\resizebox{\columnwidth}{!}{
\begin{tikzpicture}
    \node [block] (main) {{\tt main} \\ $[\cdot]$};
    \node [block, above right=0cm and 0.4cm of main] (id1) {{\tt id}\\$[8]$};
    \node [block, below right=0cm and 0.4cm of main] (id2) {{\tt id}\\$[9]$};
    \node [block, right=0.4cm of id1] (id3) {{\tt id} \\$[8,4]$};
    \node [block, right=0.4cm of id2] (id4) {{\tt id} \\$[9,4]$};
    \node [block2, right=0.4cm of id3] (id5) {{\tt id}\\$[\underbrace{8,4,\cdots,4}_k]$};
    \node [block2, right=0.4cm of id4] (id6) {{\tt id}\\$[\underbrace{9,4,\cdots,4}_k]$};
    \node [block2, below right=0cm and 0.4cm of id5] (id7) {{\tt id} \\$[\underbrace{4,\cdots,4}_{k}]$};

    \path [line] (main) -- (id1);
    \path [line] (main) -- (id2);
    \path [line] (id1) -- (id3);
    \path [line] (id2) -- (id4);
    \path [line, dashed] (id3) -- (id5);
    \path [line, dashed] (id4) -- (id6);
    \path [line] (id5) -- (id7);
    \path [line] (id6) -- (id7);
    \path [line] (id7) edge[loop above] ();
\end{tikzpicture}
}
\end{center}


%%% 2-CFA
% \begin{center}
% \resizebox{\columnwidth}{!}{
% \begin{tikzpicture}
%     \node [block] (main) {{\tt main} \\ $[\cdot]$};
%     \node [block, above right=0cm and 0.4cm of main] (id1) {{\tt id}\\$[8]$};
%     \node [block, below right=0cm and 0.4cm of main] (id2) {{\tt id}\\$[9]$};
%     \node [block, right=0.4cm of id1] (id3) {{\tt id} \\$[8,4]$};
%     \node [block, right=0.4cm of id2] (id4) {{\tt id} \\$[9,4]$};
%     \node [block, below right=0cm and 0.4cm of id3] (id7) {{\tt id} \\$[4,4]$};

%     \path [line] (main) -- (id1);
%     \path [line] (main) -- (id2);
%     \path [line] (id1) -- (id3);
%     \path [line] (id2) -- (id4);
%     \path [line] (id3) -- (id7);
%     \path [line] (id4) -- (id7);
%     \path [line] (id7) edge[loop above] ();
% \end{tikzpicture}
% }
% \end{center}
\caption{Call-graph by $k$-CFA}

\vspace{2ex}

\begin{center}
\resizebox{0.5\columnwidth}{!}{
\begin{tikzpicture}
    \node [block] (main) {{\tt main}\\$[\cdot]$};
    \node [block, above right=0cm and 0.5cm of main] (id1) {{\tt id}\\$[8]$};
    \node [block, below right=0cm and 0.5cm of main] (id2) {{\tt id}\\ $[9]$};

    \path [line] (main) -- (id1);
    \path [line] (main) -- (id2);

    \path [line] (id1) edge[loop right] ();
    \path [line] (id2) edge[loop right] ();
\end{tikzpicture}
}
\end{center}
\caption{Call-graph by 1-CFA with tunneling}
\end{subfigure}\qquad
\caption{Example and call-graphs constructed by the conventional 2-call-site sensitivity (2-CFA) and our 1-call-site-sensitivity with tunneling}
\label{fig:overview}
\end{figure}

\myparagraph{Conventional Context-Sensitive Analysis}


The conventional $k$-call-site-sensitive analysis fails to prove the queries no matter what $k$ value is used.
Because the value of \texttt{i} can be any integer, the following set $K_{\infty}$ of infinite number of call-strings can be generated for method \texttt{id} at runtime:
\[
K_{\infty} = \myset{[8], [9], [8,4], [9,4], [8,4,4], [9,4,4], [8,4,4,4], [9,4,4,4], \dots}
\]
where, for example, $[8,4]$ denotes the context that method \texttt{id} was called along the sequence of call-sites 8 and 4. The $k$-call-site-sensitive analysis approximates the call-strings in $K_{\infty}$ by their suffixes of length up to $k$. For example, when $k=2$, the analysis uses the following set $K_2$ of abstract contexts:
\[
K_2 = \myset{[8], [9], [8,4], [9,4], [4,4]}
\]
where an infinite number of contexts, $\myset{[8,4,4], [9,4,4], [8,4,4,4], [9,4,4,4],\dots}$, in $K_{\infty}$ are approximated by their common suffix $[4,4]$. The analysis analyzes the method \texttt{id} separately for each context in $K_2$. % producing the call-graph in Fig.~\ref{fig:overview}(b).
Although this approximation ensures termination, the analysis is now unable to differentiate the two separate calls to \texttt{id} at lines 8 and 9, causing the argument {\tt v} of {\tt id} to point to both objects {\tt A} and {\tt B} at the same time when the context is $[4,4]$. Thus, both objects get returned to both queries simultaneously, making the analysis fail to prove their cast safety.
Note that the analysis fails to prove the queries for any $k$ values, because all the context strings longer than $k$ are eventually
merged into a single context $[\underbrace{4,\dots,4}_{k}]$ (see Fig.~\ref{fig:overview}(b)).


\myparagraph{The Idea of Context Tunneling}

With context tunneling, however, even $1$-call-site sensitive analysis
becomes to prove the queries.
% Our idea to improve the analysis is to identify and maintain important
% context elements only.
The main weakness of the conventional
$k$-context-sensitive analysis is that it blindly updates the context
of a method at every call-site, thereby allowing important context
elements for the method to be easily overwritten by less important
ones.  In the example, distinguishing the two call-sites
at lines 8 and 9 is essential to proving the queries. However, this
information is eventually lost by repeatedly appending the less
important call-site 4 to the context of {\tt id}
(Fig.~\ref{fig:overview}(b)).
Our technique aims to overcome this weakness by maintaining important
context elements only during analysis. For example, we exclude the
call-site 4 from the context strings generated for method {\tt id} and
thus approximate the set $K_{\infty}$ to the set $K_T$ of contexts:
\[
K_T = \myset{[8], [9]}.
\]
Here abstract contexts $[8]$ and $[9]$ in $K_{T}$ denote the sets of concrete contexts
$\myset{[8], [8,4], [8,4,4], \dots}$ and
$\myset{[9], [9,4], [9,4,4], \dots}$ in $K_{\infty}$, respectively. The resulting
context-sensitive analysis with $K_{T}$ is able to prove the queries as it differentiates the two calls
to {\tt id} at lines 8 and 9 completely, producing the call-graph in
Fig.~\ref{fig:overview}(c).

% With context tunneling, however, even $1$-call-site sensitive analysis
% is able to prove the queries.


This example shows that the idea of context tunneling is potentially
powerful; even $1$-context-sensitivity with
tunneling can be as precise as
$\infty$-context-sensitivity. The goal of this paper is to maximize
this tremendous, yet untapped, potential of the existing $k$-context-sensitive analysis.

\myparagraph{Challenge}

However, achieving effective context tunneling is
challenging. The effectiveness of the technique is very sensitive
to the choice of important context elements.  For example,
choosing the call-site 4, rather than call-sites 8 and 9, as important does not
work for the example program.  In the worst case, the analysis
precision degenerates into the context-insensitive case (e.g. when
selecting no context elements at all), becoming even inferior to the
ordinary
$k$-context-sensitive analysis.  As a result, coming up with a good
heuristic rule for choosing important context elements is nontrivial;
hand-crafting such a rule not only requires a huge amount of
engineering effort and domain knowledge but also likely fails to
maximize the potential of the technique.
% adaptable as a fixed heuristic rule tuned for a particular situation
% may not be effective for other programs, analyses, or queries.

%\input{overview_learning}

\begin{comment}
\begin{figure}
\begin{tikzpicture}
\node [block] (main) {{\tt main} \\ $[\cdot]$};
\node [block, below left=0.4cm and -0.5cm of main] (id_1) {{\tt id} \\ $[21]$};
\node [block, left=0.4cm of id_1] (id_2) {{\tt id} \\ $[20]$};
\node [block, left=0.4cm of id_2] (id_3) {{\tt id} \\ $[19]$};
\node [block, left=0.4cm of id_3] (id_4) {{\tt id} \\ $[18]$};
\node [block, below right=0.4cm and -0.5cm of main] (id1_1) {{\tt id1} \\ $[23]$};
\node [block, below=0.4cm of id1_1] (id_5) {{\tt id} \\ $[23]$};
\node [block, right=0.4cm of id1_1] (id1_2) {{\tt id1} \\ $[24]$};
\node [block, below=0.4cm of id1_2] (id_6) {{\tt id} \\ $[24]$};
\node [block, right=0.4cm of id1_2] (id2_1) {{\tt id2} \\ $[26]$};
\node [block, below=0.4cm of id2_1] (idrec_1) {{\tt idrec} \\ $[26]$};
\node [block, right=0.4cm of id2_1] (id2_2) {{\tt id2} \\ $[27]$};
\node [block, below=0.4cm of id2_2] (idrec_2) {{\tt idrec} \\ $[27]$};

\path [line] (main) -- (id_1);
\path [line] (main) -- (id_2.north);
\path [line] (main) -- (id_3.north);
\path [line] (main) -- (id_4.north);
\path [line] (main) -- (id1_1);
\path [line] (id1_1) -- (id_5);
\path [line] (main) -- (id1_2.north);
\path [line] (id1_2) -- (id_6);
\path [line] (main) -- (id2_1.north);
\path [line] (id2_1) -- (idrec_1);
\path [line] (idrec_1) edge[loop below] ();
\path [line] (main) -- (id2_2.north);
\path [line] (id2_2) -- (idrec_2);
\path [line] (idrec_2) edge[loop below] ();
\end{tikzpicture}
\caption{Call-graph of code in Figure~\ref{fig:overview:new} from $\onecallHT$ analysis with context tunneling relations $\TunnelingRelation=\myset{({\tt id1}, *), (*, {\tt idrec})}$. Symbol $*$ can be any methods.}
\end{figure}

\begin{figure}
\begin{tikzpicture}
\node [block] (main) {{\tt main} \\ $[\cdot]$};
\node [block, below left=0.4cm and -0.5cm of main] (id_1) {{\tt id} \\ $[21]$};
\node [block, left=0.4cm of id_1] (id_2) {{\tt id} \\ $[20]$};
\node [block, left=0.4cm of id_2] (id_3) {{\tt id} \\ $[19]$};
\node [block, left=0.4cm of id_3] (id_4) {{\tt id} \\ $[18]$};
\node [block, below right=0.4cm and -0.5cm of main] (id1_1) {{\tt id1} \\ $[23]$};
\node [block, below right=0.4cm and -0.4cm of id1_1] (id_5) {{\tt id} \\ $[10]$};
\node [block, right=0.4cm of id1_1] (id1_2) {{\tt id1} \\ $[24]$};

\node [block, right=0.4cm of id1_2] (id2_1) {{\tt id2} \\ $[26]$};
\node [block, below right=0.4cm and -0.4cm of id2_1] (idrec_1) {{\tt idrec} \\ $[13]$};
\node [block, right=0.4cm of id2_1] (id2_2) {{\tt id2} \\ $[27]$};
\node [block, below=0.4cm of idrec_1] (idrec_2) {{\tt idrec} \\ $[7]$};

\path [line] (main) -- (id_1);
\path [line] (main) -- (id_2.north);
\path [line] (main) -- (id_3.north);
\path [line] (main) -- (id_4.north);
\path [line] (main) -- (id1_1);
\path [line] (id1_1) -- (id_5);
\path [line] (main) -- (id1_2.north);
\path [line] (id1_2) -- (id_5);
\path [line] (main) -- (id2_1.north);
\path [line] (id2_1) -- (idrec_1);
\path [line] (main) -- (id2_2.north);
\path [line] (id2_2) -- (idrec_1);
\path [line] (idrec_1) -- (idrec_2);
\path [line] (idrec_2) edge[loop right] ();


\end{tikzpicture}
\caption{Call-graph of code in Figure~\ref{fig:overview:new} with from conventional $\onecallH$ analysis.}
\end{figure}
\end{comment}
%%% Local Variables:
%%% mode: latex
%%% TeX-master: "paper"
%%% End:
