\chapter{Data-driven Context Tunneling}\label{sec:Tunneling}
  In this chapter, we present our novel technique context tunneling and our data-driven approach for learning context tunneling heuristics.
  As context-sensitivity holds the key to the development
  of precise and scalable pointer analysis, a variety of techniques
  for context-sensitivity have been proposed. However, existing
  approaches such as $k$-call-site-sensitivity or $k$-object-sensitivity have a
  significant weakness that they unconditionally update the context of a
  method at every call-site, allowing important context elements to be
  overwritten by more recent, but not necessarily more important,
  context elements. In this chapter, we show that this is a key limiting factor of
  existing context-sensitive analyses, and demonstrate that remarkable increase in
  both precision and scalability can be gained by
  maintaining important context elements only.
  Our approach, called context tunneling, updates contexts selectively
  and decides when to propagate the same context without
  modification.



  We attain context tunneling via a data-driven approach.  The
  effectiveness of context tunneling is very sensitive to the choice
  of important context elements. Even worse, precision is not
  monotonically increasing with respect to the ordering of the
  choices. As a result, manually coming up with a good heuristic rule
  for context tunneling is extremely challenging and likely fails to
  maximize its potential. We address this challenge by developing a
  specialized data-driven algorithm, which is able to automatically
  search for high-quality heuristics over the non-monotonic space of
  context tunneling.

  We implemented our approach in the Doop framework and applied it to
  four major flavors of context-sensitivity: call-site-sensitivity,
  object-sensitivity, type-sensitivity, and hybrid context-sensitivity. In
  all cases, $1$-context-sensitive analysis with context
  tunneling far outperformed deeper context-sensitivity with $k=2$ in
  both precision and scalability.


\definecolor{dkgreen}{rgb}{0,0.6,0}
\definecolor{gray}{rgb}{0.5,0.5,0.5}
\definecolor{mauve}{rgb}{0.58,0,0.82}

\lstset{,language=Java, aboveskip=3mm, belowskip=3mm,
	showstringspaces=false, columns=flexible,
	basicstyle=\linespread{1.2}\small\ttfamily, numbers=left, numbersep=5pt,
	numberstyle=\small\color{gray}, keywordstyle=\color{blue},
	commentstyle=\color{dkgreen}, stringstyle=\color{mauve},
	breaklines=true, breakatwhitespace=true, tabsize=3 
}



% \tikzstyle{block} = [rectangle, draw, fill=white, text width=5em,
% text centered, rounded corners, minimum height=4em]

\tikzstyle{block} = [rectangle, draw, fill=white, text width=2.8em,
, text
centered, rounded corners, minimum height=3em]

%\tikzstyle{block2} = [rectangle,   text width=2em, text
%centered, rounded corners, minimum height=3em]

\tikzstyle{block2} =
[rectangle, draw, fill=white, text width=5em, text centered, rounded
corners, minimum height=4em, minimum width = 6em] \tikzstyle{line} = [draw, -latex']
\tikzstyle{onlyText} = [text width =2em, text centered]




\tikzstyle{myCircle} = [circle,thick,draw=black!75   text width=3.5em, text
centered, minimum height=3em]



\tikzstyle{line} = [draw, -latex']
\tikzstyle{onlyText} = [text width =5em, text centered]
\tikzstyle{smallOnlyText} = [text width =15em, text centered]
\tikzstyle{None} = [text width =0em, text centered]
\tikzstyle{longText} = [text width = 20em, text centered]

%\setcopyright{rightsretained}


\tikzstyle{block4} =
[rectangle, draw, fill=white, text width=9.5em, text centered, rounded
corners, minimum height=2.3em]
\tikzstyle{block3} =
[rectangle, draw, fill=white, text width=8em, text centered, rounded
corners, minimum height=2.3em] \tikzstyle{line} = [draw, -latex']


\tikzstyle{blocks} = [rectangle, draw, fill=white, text width=0.7cm, text
centered,  text width=4em, rounded corners, minimum height=0.5cm]











\input{ContextTunneling/introduction}
\input{ContextTunneling/overview_new3}
\input{ContextTunneling/tunneling}
\input{ContextTunneling/learning}
\input{ContextTunneling/evaluation}
%\input{ContextTunneling/validity}
%
%Context-sensitivity holds the key to the development of precise and
%scalable pointer analysis. In order to accurately track local
%variables and heap objects, a context-sensitive analysis treats
%multiple calls to the same method separately for its different calling
%contexts.  For object-oriented and functional languages,
%context-sensitivity is the single most important factor that affects
%both precision and scalability.  It has greater impact on the analysis
%precision than other techniques such as
%flow-sensitivity~\cite{Lhotak2006,Smaragdakis2015}, and the improved
%precision by context-sensitivity is likely to increase scalability as
%well~\cite{Smaragdakis2011, Kashyap2014}.
%
%
