% !TEX root = ./paper.tex
\clearpage
\newtheorem{openquestion}{Question}

\section{Open Question: Is Complete Simulation Possible?}

\subsection{High Level Description}

The observation in Section~\ref{sec:counter_example}, that there exists
a counter-example in our setting (tunneling abstraction space is a set
of invocation site) but the counter-example is not the case in a more
generalized abstraction space of context tunneling (pairs of
invocation and receiver object), lead us to the following open question.
%\begin{equation}
\begin{openquestion}\label{openQ}
Can we define a tunneling abstraction space $S$ (e.g., pairs of receiver
object and invocation site) that $k$-call-site sensitivity with
tunneling can always become equal or more precise than $k$-object
sensitivity with tunneling?
\end{openquestion}
%\end{equation}
If the above question is true (we can define such tunneling
abstraction space), $k$-call-site sensitivity is theoretically more
precise than $k$-object sensitivity when k-limited context sensitivity
is generalized with context tunneling. The formal description of the
open question is described in Section~\ref{sec:quextion:formal}. 

% (in flow-insensitive but context sensitive pointer analysis)

Note that the converse is not true; it is unable to define a tunneling
abstraction space $S$ that $k$-object sensitivity with
tunneling can always become equal or more precise than $k$-call-site
sensitivity with tunneling. The example code in
Figure~\ref{background:example2} is a counter-example for an arbitrary
tunneling abstraction space. By the definition of context tunneling
(determine whether to update context or not), the method
{\tt id} in the example (Figure~\ref{background:example2}) can have
the the contexts \texttt{[D]} (update context) or \texttt{[$\cdot$]}
(inherit context) no matter what tunneling abstraction space is
used. $k$-object sensitivity with tunneling is unable to separate the
three method calls (invoked at the three different invocation sites)
with the two 
available contexts. k-call-site sensitivity, however, can separate the
three method calls with a tunneling abstraction $\emptyset \subseteq
S$ (always update contexts) for all tunneling abstraction space
$S$ of context tunneling. 


In this paper, we showed a set of invocation sites is practically (not
theoretically) the abstraction space ($T \subseteq \Invo$) that
k-call-site sensitivity with tunneling can simulate k-object
sensitivity with tunneling. Our future work 
is answering the {\sc Question~\ref{openQ}} to show that
call-site sensitivity is theoretically more precise than
object-sensitivity (the answer of the question is ``yes'') or the two
contexts are still incomparable in the generalized k-limited context
sensitivity (the answer is ``no''). 

%What we show in our paper is that invocation sites 




\subsection{Formal Description}~\label{sec:quextion:formal}
Let $F_{P,k}^{T, \updatectx}$ be the analysis uses the context update
function $\updatectx$, context depth $k\in\mbn$, tunneling abstraction
$T \subseteq S$ for analyzing the program $P$:
\begin{equation}\label{eq:analysis}
F_{P,k}^{T, \updatectx}(\ptsto, \reachable, \callgraph) = \bigsqcup_{\inst \in \Inst_P}
f_{k, \inst}^{T, \updatectx}(\ptsto,
\reachable, \callgraph)
\end{equation}
where $f_{k, \inst}^{T, \updatectx}$ is the transfer function (simply described
as $f_l$ in Section~\ref{sec:setting}) encoding
the abstract semantics of instructions. Running the analysis is to compute the least fixed point of
$F^{T, \updatectx}_{P,k}$:
\begin{equation}\label{eq:fixpoint}
  \fix F_{P,k}^{T, \updatectx} = F^{T, \updatectx}_{P,k}
  (\bot_\ptsto, \bot_\reachable,\bot_\callgraph) \sqcup F^{T, \updatectx}_{P,k}  (F^{T, \updatectx}_{P,k}
  (\bot_\ptsto, \bot_\reachable,\bot_\callgraph)) \sqcup \cdots
\end{equation}
where we define the bottom elements for the domains as follows:
\[
  \bot_\ptsto = \lambda (x,c).\emptyset, \qquad \bot_\reachable =
\lambda m. \left\{ \begin{array}{ll} \myset{\epsilon} & \mbox{if}~m =
                                                        \entry_P \\
                     \emptyset & \mbox{otherwise} \end{array} \right., \qquad
  \bot_\callgraph = \emptyset,
\]
%Note that the reachability map ($\reachable$) initially
%associates the entry method with the initial context
%$\epsilon$. 
The fixed point computation in (\ref{eq:fixpoint})
eventually stabilizes because the domains are
finite and the transfer function is monotone.




\myparagraph{Order of Analysis Precision}
 For two analyses $F_{P,k}^{T, \updatectx}$ and
 $F_{P,k'}^{T',\updatectx'}$ for program $P$, we say the former is more
 precise than (or equal to) the
 latter, denoted $F_{P,k}^{T, \updatectx} \moreprecise F_{P,k'}^{T', \updatectx'}$, if and only if
 \[
   \project(\fix F_{P,k}^{T, \updatectx}) \sqsubseteq \project(\fix F_{P,k'}^{T', \updatectx'})
 \]
 where $\project$ extracts the context-insensitive points-to
 information from the analysis result $(\ptsto, \reachable,\callgraph)$:
 \begin{equation}\label{eq:project}
 \project(X, R,\callgraph) = \lambda x.\; \bigsqcup_{\ctx \in \Ctx}
 \myset{h \mid (h, \hctx) \in X(x, \ctx)},
 \end{equation}
and the order between the two projected analysis results is defined as follows:
 \[
   \project(\fix F_{P,k}^{T, \updatectx}) \sqsubseteq \project(\fix
   F_{P,k'}^{T', \updatectx'}) \iff \forall x\in \Var_P. \project(\fix
   F_{P,k}^{T, \updatectx})(x) \subseteq \project(\fix
   F_{P,k'}^{T', \updatectx'}) (x).
 \]
That is, an analysis is more precise than the other if it produces
a strictly smaller points-to set for all variables.


Now we formalize the open question. 
Answering ``yes'' to the {\sc Question~\ref{openQ}} equals to show that the
following proposition holds:
\newtheorem{prop}{Proposition}
\begin{prop}
Let $\updatectx_{\it obj}$
and $\updatectx_{\it call}$ be the context functions for
object-sensitivity and call-site-sensitivity given in
(\ref{eq:objsens}) and (\ref{eq:cfa}), respectively. 
\begin{equation}\label{eq:conjecture}
\exists S. \; \forall P. \; \forall k\in \mbn. \; \forall T_{\it obj}\in S. \; \exists
T_{\it call} \in S. \; 
F_{P,k}^{T_{\it call},\updatectx_{{\it call}}}
\moreprecise F_{P,k}^{T_{\it obj}, \updatectx_{{\it obj}}}.
\end{equation}
\label{conjecture}
\end{prop}
That is, we can define a tunneling abstraction space $S$ that
for a given program $P$, context depth $k$, and tunneling abstracion for
object sensitivity $T_{\it obj} \in S$, we can find a
corresponding tunenling abstraction for call-site sensitivity $T_{\it
  call} \in S$ that make $k$-call-site sensitivity with tunneling
($F_{P,k}^{T_{\it call},\updatectx_{{\it call}}}$) produce a more
precise analysis result than the
given object sensitivity with tunneling ($F_{P,k}^{T_{\it obj},
  \updatectx_{{\it obj}}}$).
If there is no such abstraction space (the answer to {\sc
  Question~\ref{openQ}} is ``no''), call-site sensitivity and 
object sensitivity are still incomparable in the generalized
k-limited context sensitivity
(we already showed it is unable to define a
tunneling space that 
object sensitivity with tunneling can always become equal or more
precise than call-site sensitivity). 


%%% Local Variables:
%%% mode: latex
%%% TeX-master: "paper"
%%% End:
